Combined single-cell transcriptomics and virus sequencing of influenza infections that trigger innate immunity

### 2018-09-20 paper/paper.tex
slight edits to Methods, then realized better to wait until figures made

@@

Both viral strains were generated by reverse genetics using the pHW18* series of bi-directional plasmids~\citep{hoffmann2000dna}.
We controlled the durations and MOI during viral passaging since these factors can greatly affect the accumulation of defective viral particles~\citep{xue2016propagation}.
The viruses were generated by reverse genetics in co-cultures of 293T and MDCK-SIAT1 in influenza growth media and then propagated in MDCK-SIAT1 cells in influenza growth media using the same basic procedures detailed in \citet{russell2018extreme}.
Specifically, after generation by reverse genetics, the wildtype variant was expanded at an MOI of 0.001 for 72 hours twice in MDCK-SIAT1 cells, and the synonymously barcoded variant was expanded once at an MOI of 0.01 for 60 hours.
The MOIs for this passaging are based on titers determined using TCID50 assays via the formula of \citet{reed1938simple} as implemented at \url{https://github.com/jbloomlab/reedmuenchcalculator}.

@@

\subsection{Viruses for validation experiments}

All viruses were generated using reverse-genetics as previously described using plasmids derived from pHW181-PB2, pHW182-PB1, pHW183-PA, pHW184-HA, pHW185-NP, pHW186-NA, pHW187-M, and pHW188-NS~\citep{hoffmann2000dna}.
To generate viruses from these plasmids, or variants described below, we transfected an equimolar mix of all eight plasmids into cocultures of 293T and MDCK-SIAT1 cells seeded at a ratio of 8:1. At 24 hr post-transfection, we changed media from D10 to influenza growth media (Opti-MEM supplemented with 0.01\% heat-inactivated FBS, 0.3\% BSA, 100 U of penicillin/ml, 100 $\mu$g of streptomycin/ml, and 100 $\mu$g of calcium chloride/ml). At 48-72h post-transfection we harvested the virus-containing supernatant, pelletted cellular material by centrifugation at 300 x g's for 4 min, and stored aliquots of the clarified viral supernatant at -80$^{\circ}$C.
We then titered thawed aliquots of viral by TCID50 on MDCK-SIAT1 cells, computing titers via the formula of Reed and Muench as described above.

>>>>

%%% begin validation figure %%%
\begin{figure}

\jdbcomment{add figure}
\caption{\jdbcomment{add caption}}
\label{fig:validation}

\figdata{Genbank plasmid maps for the mutant genes in this figure cloned into the pHW* bi-directional reverse genetics plasmid~\citep{hoffmann2000dna} are at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/tree/master/paper/figures/FluVariantPlasmidMaps}}
\label{figdata:sequences}

\end{figure}
%%% end validation figure %%%

@@

Both viral strains were generated by reverse genetics using the pHW18* series of bi-directional plasmids~\citep{hoffmann2000dna}.
We controlled the durations and MOI during viral passaging since these factors can greatly affect the accumulation of defective viral particles~\citep{xue2016propagation}.
The viruses were generated by reverse genetics in co-cultures of 293T and MDCK-SIAT1 in influenza growth media ((Opti-MEM supplemented with 0.01\% heat-inactivated FBS, 0.3\% BSA, 100 U of penicillin/ml, 100 $\mu$g of streptomycin/ml, and 100 $\mu$g of calcium chloride/ml) and then propagated in MDCK-SIAT1 cells in influenza growth media using the same basic procedures detailed in \citet{russell2018extreme}.
Specifically, after generation by reverse genetics, the wildtype variant was expanded at an MOI of 0.001 for 72 hours twice in MDCK-SIAT1 cells, and the synonymously barcoded variant was expanded once at an MOI of 0.01 for 60 hours.
The MOIs for this passaging are based on titers determined using TCID50 assays via the formula of \citet{reed1938simple} as implemented at \url{https://github.com/jbloomlab/reedmuenchcalculator}.

@@

\subsection{Viruses for validation experiments}
We generated the mutant viruses for the validation experiments in \FIG{validation} by reverse genetics using the pHW18* series of WSN reverse genetics plasmids~\citep{hoffmann2000dna}, but substituting the appropriate mutant plasmid listed in \FIGDATA[validation]{sequences} for the wildtype plasmid for that gene.
To generate the viruses from these plasmids, we transfected an equimolar mix of all eight plasmids into co-cultures of 293T and MDCK-SIAT1 cells seeded at a ratio of 8:1.
At 24 hours post-transfection, we changed media from D10 to influenza growth media. 
At 48 to 72 hours post-transfection, we harvested the virus-containing supernatant, clarified this supernatant by centrifugation at 300$\times$g for 4 min, and stored aliquots of the clarified viral supernatant at -80$^{\circ}$C.
We then thawed an aliquot of each virus and titered by TCID50 as described above.
